### 2023-09-04 paper/sec-pheno.tex
Update sec-pheno.tex

\section{Implications for HL-LHC processes}
\label{sec:pheno}

The reduction of PDF uncertainties enabled by the neutrino DIS measurements
at the FPF presented in Sect.~\ref{sec:protonPDFs}
makes possible more precise theoretical predictions for key processes at the
HL-LHC.
%
Here we present an initial study of the phenomenological implications
of PDFs enhanced with LHC neutrino data.
%
We adopt the same settings as in the LHC phenomenology analysis presented
in the PDF4LHC21 combination paper~\cite{PDF4LHCWorkingGroup:2022cjn} and provide predictions
both for inclusive fiducial cross-sections and for differential distributions.
%
Specifically, we present results for 
single and double gauge boson production, inclusive top quark pair production,
and Higgs production in gluon
fusion and in association with a vector boson.
%
We evaluate these cross-sections using NLO matrix elements
which include  both in the
QCD and electroweak corrections using
{\sc\small mg5\_amc@nlo}~\cite{Frederix:2018nkq}
interfaced to {\sc\small PineAPPL}~\cite{Carrazza:2020gss}.
%
For all processes, realistic selection and acceptance cuts on the final state particles
have been applied, and PDF uncertainty bands correspond to 90\% CL
uncertainties.
%
No further theory uncertainties are considered in this
analysis.

Fig.~\ref{fig:NNPDF40_pheno_integrated} displays
fiducial cross-section for representative LHC processes at $\sqrt{s}=14$ TeV
evaluated with NNPDF4.0 NNLO, compared with the fits including the FPF structure function projections.
%
For the latter, we display the variants based only on statistical uncertainties and that
which includes also systematic errors.
%
The central values are set to be the same as in the original NNPDF4.0 calculation in all cases.
%
See~\cite{NNPDF:2021njg} for the calculational settings.
%
From top to bottom, we show inclusive Drell-Yan production ($Z, W^+, W^-$), Higgs production
in vector-boson fusion, Higgs associated
production, and diboson production ($W^+W^-$, $W^+Z$, $W^-Z$).
%
We focus on processes dominated by quark-quark and quark-antiquark scattering, given
that the FPF structure functions would not have any impact on gluon-initiated
processes such as top quark pair production or Higgs production in gluon fusion.
%
The corresponding comparison at the level of differential distributions
are shown in Fig.~\ref{fig:NNPDF40_pheno_differential}.
%
As done for the fiducial cross-sections of Fig.~\ref{fig:NNPDF40_pheno_integrated},
we only indicate the relative PDF uncertainty in each fit, with central values
assumed to be the same by construction.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_DY_14TEV_40_PHENO-integrated.pdf}
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WM_14TEV_40_PHENO-integrated.pdf}
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WP_14TEV_40_PHENO-integrated.pdf}
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HVBF_14TEV_40_PHENO-integrated.pdf}
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HWP_14TEV_40_PHENO-integrated.pdf}
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HWM_14TEV_40_PHENO-integrated.pdf}
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WPWM_14TEV_40_PHENO-integrated.pdf}
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WPZ_14TEV_40_PHENO-integrated.pdf}
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-integrated.pdf}
\caption{Fiducial cross-sections for representative LHC processes at $\sqrt{s}=14$ TeV
evaluated with NNPDF4.0 NNLO, compared with the fits including the FPF structure function projections.
%
For the NNPDF4.0 baseline
prediction, the dark (light) bands indicate the 68\% (95\%) CL uncertainties.
%
The fit labelled as ``\_FPF'' is the one  based on statistical uncertainties,
while that labelled as ``\_FPF$^*$'' also includes systematic errors.
%
The central values are set to be the same as in the original NNPDF4.0 calculation in all cases.
%
See~\cite{NNPDF:2021njg,PDF4LHCWorkingGroup:2022cjn} for the calculational settings.
%
From top to bottom, we show inclusive Drell-Yan production ($Z, W^+, W^-$), Higgs production
in vector-boson fusion, Higgs associated
production, and diboson production ($W^+W^-$, $W^+Z$, $W^-Z$).
%
}
\label{fig:NNPDF40_pheno_integrated}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_DY_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WM_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WP_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HVBF_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HWP_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HWM_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WPWM_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WPZ_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-global.pdf}
\caption{Same as Fig.~\ref{fig:NNPDF40_pheno_integrated}
for the corresponding differential distributions.
%
}
\label{fig:NNPDF40_pheno_differential}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
	\centering
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_DY_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WM_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WP_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HVBF_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HWP_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HWM_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WPWM_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WPZ_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
	\caption{
		Same as Fig.~\ref{fig:NNPDF40_pheno_integrated} but with PDF4LHC21.
		}
	\label{fig:PDF4LHC21_pheno_integrated}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\section{Implications for Higgs and weak boson production}
\label{sec:pheno}

The reduction of PDF uncertainties made possible by neutrino DIS measurements
at the FPF, discussed in Sect.~\ref{sec:protonPDFs},
enables more precise theoretical predictions for core processes at the
HL-LHC.
%
Here we present an initial study of the phenomenological implications
of the PDFs enhanced with LHC neutrino data
for hard-scattering processes at proton colliders.
%
Specifically, we present results for 
single and double gauge boson production,  Higgs production in
vector-boson fusion, and Higgs production and in association with a vector boson.
%
We focus on processes sensitive to the quark-quark and quark-antiquark initial
states, given that LHC neutrinos do not provide information on the gluon
PDF and hence they cannot inform  gluon-initiated
processes, such as top quark pair production or Higgs production in gluon fusion.

We adopt the same calculational settings as in the LHC phenomenology analysis considered
in the PDF4LHC21 combination study~\cite{PDF4LHCWorkingGroup:2022cjn} and provide predictions
both for inclusive cross-sections, integrated in the fiducial
region, and for differential distributions.
%
We evaluate these cross-sections using matrix elements
which include NLO corrections both in the
QCD and electroweak coupling using
{\sc\small mg5\_amc@nlo}~\cite{Frederix:2018nkq}
interfaced to {\sc\small PineAPPL}~\cite{Carrazza:2020gss}.
%
For all processes, realistic selection and acceptance cuts on the final state particles
have been applied.
%
No further theory uncertainties are considered in this
analysis, given that we don't aim to compare with experimental data.

Fig.~\ref{fig:NNPDF40_pheno_integrated} displays
fiducial cross-section for representative LHC processes at $\sqrt{s}=14$ TeV
evaluated with NNPDF4.0 (top panels)
and with PDF4LHC21 (bottom panels),
compared with the results obtained from
the fits including the FPF structure function projections.
%
For the latter, we display the variants based only on statistical uncertainties and that
which includes also systematic errors.
%
The central values are set to be the same as in the original NNPDF4.0 calculation in all cases.
%
See~\cite{NNPDF:2021njg} for the calculational settings.
%
From top to bottom, we show inclusive Drell-Yan production ($Z, W^+, W^-$), Higgs production
in vector-boson fusion, Higgs associated
production, and diboson production ($W^+W^-$, $W^+Z$, $W^-Z$).
%
The corresponding comparison at the level of differential distributions
are shown in Fig.~\ref{fig:NNPDF40_pheno_differential}.
%
As done for the fiducial cross-sections of Fig.~\ref{fig:NNPDF40_pheno_integrated},
we only indicate the relative PDF uncertainty in each fit, with central values
assumed to be the same by construction.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_DY_14TEV_40_PHENO-integrated.pdf}
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WM_14TEV_40_PHENO-integrated.pdf}
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WP_14TEV_40_PHENO-integrated.pdf}
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HVBF_14TEV_40_PHENO-integrated.pdf}
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HWP_14TEV_40_PHENO-integrated.pdf}
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HWM_14TEV_40_PHENO-integrated.pdf}
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WPWM_14TEV_40_PHENO-integrated.pdf}
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WPZ_14TEV_40_PHENO-integrated.pdf}
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-integrated.pdf}
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_DY_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WM_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WP_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HVBF_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HWP_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HWM_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WPWM_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WPZ_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
\caption{Fiducial cross-sections for representative LHC processes at $\sqrt{s}=14$ TeV
  evaluated with NNPDF4.0 (upper panels) and PDF4LHC21 (bottom panels),
  compared with the fits including the FPF structure function projections.
  %
  See~\cite{NNPDF:2021njg,PDF4LHCWorkingGroup:2022cjn} for the calculational settings
  used to evaluate these cross-sections.
%
For the baseline
predictions, the dark (light) bands indicate the 68\% (95\%) CL uncertainties.
%
The fits labelled as ``\_FPF'' are the ones considering statistical uncertainties,
while those labelled as ``\_FPF$^*$'' also include systematic errors.
%
In the fits with FPF data, the central values are set to be the same as
in the corresponding baseline.
%
We provide predictions for inclusive Drell-Yan production ($Z, W^+, W^-$), Higgs production
in vector-boson fusion, Higgs associated
production, and diboson production ($W^+W^-$, $W^+Z$, $W^-Z$).
%
}
\label{fig:NNPDF40_pheno_integrated}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_DY_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WM_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WP_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HVBF_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HWP_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HWM_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WPWM_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WPZ_14TEV_40_PHENO-global.pdf}
\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-global.pdf}
\caption{Same as Fig.~\ref{fig:NNPDF40_pheno_integrated}
for the corresponding differential distributions in the case of NNPDF4.0
%
}
\label{fig:NNPDF40_pheno_differential}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@
